Inferring Galactic Parameters from Chemical Abundances with Simulation-Based Inference

### 2025-02-17 src/tex/ms.tex
[showyourwork] overleaf sync

% The ... repository, which contains code, additional documentation, and interactive dashboards, is available on GitHub.%\footnote{URL: \url{https://github.com/bGuenes/sbi_chemical_abundances}}

\section{Simulation-based calibration}
\label{sec:sbc}

@@

TARP \citep{Lemos2023} is an alternative calibration check. Given a test set $(\theta^*,x^*)$ and a set of reference points $\theta_r$, TARP calculates statistics for posterior calibration by - drawing posterior samples $\theta$ given each observation $x^*$ and calculating the distance $r$ between $\theta^*$ and $\theta_r$ counting for how many of the posterior samples the distance to $\theta_r$ is smaller than $r$ \citep[see e.g. Fig.~2 in][for an illustration]{Lemos2023}.

@@

\end{appendix}

>>>>

\begin{figure*}[]
     \centering
     \includegraphics[width=\textwidth, trim={6cm, 0cm, 6cm, 0cm}, clip]{figures/ili_coverage.pdf}
     \includegraphics[width=\textwidth, trim={6cm, 0cm, 6cm, 0cm}, clip]{figures/ili_predictions.pdf}
     %\vspace{-.5cm}
     \caption{Top: TARP plot showing the expected coverage probability vs. the credibility level $\alpha$ for each of the six individual parameters in our inference. The dashed black 1:1-line shows an ideal calibrated posterior and the blue solid line shows the TARP value for our NPE. Bottom: }
     \label{fig:tarp}
     \script{evaluate_sbi.py}
\end{figure*}
% The ... repository, which contains code, additional documentation, and interactive dashboards, is available on GitHub.%\footnote{URL: \url{https://github.com/bGuenes/sbi_chemical_abundances}}

\section{Neural Posterior Calibration}
\label{sec:sbc}

@@

TARP \citep{Lemos2023} is an alternative calibration check for the joint distribution, for which defining a rank is not straightforward. Given a test set $(\theta^*,x^*)$ and a set of reference points $\theta_r$, TARP calculates statistics for posterior calibration by - drawing posterior samples $\theta$ given each observation $x^*$ and calculating the distance $r$ between $\theta^*$ and $\theta_r$ counting for how many of the posterior samples the distance to $\theta_r$ is smaller than $r$ \citep[see e.g. Fig.~2 in][for an illustration]{Lemos2023}.

@@

\section{Additional inference results}

\begin{figure*}
    \centering
    \includegraphics[width=\textwidth]{figures/Nstar_comp_different_prior.pdf}
    \vspace{-.5cm}
    \caption{Same as Fig.~\ref{fig:CHEMPY_TNG_N_star_analysis} but for mock data a created with parameters for $\alpha_{IMF}$ and $\log_{10}(N_{Ia})$.}
    \label{fig:N_star_analysis_different_prior}
    \script{additional_inference.py}
\end{figure*}
\end{appendix}
